---
title: "publications analysis"
author: "Masumbuko Semba"
date: "8/23/2021"
output: 
    bookdown::pdf_document2:
      latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, comment = FALSE, message = FALSE)
```

```{r}
require(ggwordcloud)
require(magrittr)
require(tidyverse)
require(tidytext)
require(wordcloud)
require(RColorBrewer)

pal <- brewer.pal(8,"Dark2")
```


# Publications

```{r}
publications = read_csv("tafiri_publication/TAFIRI Library.csv") %>% 
  select(authors:journal)

```


```{r contrib, fig.width=7, fig.height=7,fig.cap="Contribution of authors in publications"}

publications %>% 
  select(authors) %>% 
  tidytext::unnest_tokens(input = authors, output = word) %>% 
  mutate(len = str_length(string = word)) %>% 
  filter(len >3) %>% 
  select(word) %>% 
  mutate(word = str_to_title(string = word), 
         word = if_else(word == "Machumu", "Kishe", word)) %>% 
  group_by(word) %>% 
  count(sort = TRUE)%>%
  ungroup() %>% 
  top_n(200) %$% 
  ggwordcloud(words = word, 
            freq = n, 
            colors = pal, 
            max.words = 180, 
            random.order = FALSE, 
            min.freq = 3)+
  ggthemes::theme_solarized_2()

# ggsave("graphics/publication_rush.pdf", width = 7, height = 7)
```


```{r first, fig.width=7, fig.height=7,fig.cap="Contribution of authors as first author in publications"}
publications %>% 
  separate(col = authors, into = c("authors", NA), sep = " ") %>% 
  select(authors) %>% 
  tidytext::unnest_tokens(input = authors, output = word) %>% 
  mutate(len = str_length(string = word)) %>% 
  filter(len >3) %>% 
  select(word) %>% 
  mutate(word = str_to_title(string = word), 
         word = if_else(word == "Machumu", "Kishe", word)) %>% 
  group_by(word) %>% 
  count(sort = TRUE)%>%
  ungroup() %>% 
  top_n(200) %$% 
  ggwordcloud(words = word, 
            freq = n, 
            colors = pal, 
            max.words = 180, 
            random.order = FALSE, 
            min.freq = 1)+
  ggthemes::theme_solarized_2()
 
```





```{r, eval=FALSE}
# Deep sea

texta = pdftools::pdf_data("d:/semba/dsfa_fumba/project reports/Complete DMG Tuna Report.pdf" )

texta[c(18:80)] %>% 
  bind_rows() %>% 
  select(word = text) %>% 
  mutate(word = str_to_title(word),
         word_length = str_length(word)) %>% 
  filter(word_length >2 & !word %in% c("Year", "Table", "2020", "This", "What", "With", "2017", "2018",  "And", "The", "For", "Are", "From", "Have", "(Table", "Has", "Who", "Not", "Was", "Most", "Your", "Any")) %>% 
  anti_join(get_stopwords())%>% 
  group_by(word) %>% 
  count(sort = TRUE) %>% 
  ungroup() %$% 
  wordcloud(words = word,freq = n, max.words = 120, random.order = F, min.freq = 10, colors = brewer.pal(n = 8, name = "Accent"))

```
\newpage

## Google scholar publications

```{r}
require(scholar)
```

```{r}

tafiri = data.frame(
author = c("Masumbuko Semba", "Ismael A. Kimirei", "Shigalla Mahongo", "Mary Alphonce Kishe", "Emmanuel A. Sweke", "Baraka Kuguru", "Deogratias Mulokozi","Rushingisha George"),
gs.id = c("a0o574AAAAAJ","8NWslCkAAAAJ", "89jrgU8AAAAJ", "mOGizdwAAAAJ", "lAUQowgAAAAJ", "6TzNkHEAAAAJ", "aq_GimkAAAAJ", "aLpKvUQAAAAJ")
)


```

## Pull publications

```{r}
set.seed(2145)

kim.pub = scholar::get_publications(id = tafiri$gs.id[2])

kim.pub %>% 
  sample_n(size = 30)%>% 
  select(author:year) %>% 
  kableExtra::kable(format = "latex", booktab = TRUE, caption = "Articles by	IA Kimirei") %>% 
  kableExtra::kable_styling(latex_options = "hold_position", font_size = 10) %>% 
  kableExtra::landscape() 
```

\newpage
## Pull citations

```{r, fig.cap="Kimirei citation over a period"}
kim.cite = scholar::get_citation_history(id = tafiri$gs.id[2])

kim.cite %>% 
  ggplot(aes(x = year, y = cites))+
  geom_line()+
  geom_point() +
  geom_hline(yintercept = 100, color = "red", linetype = 3)+
  scale_x_continuous(breaks = seq(2004,2021,2))+
  scale_y_continuous(breaks = seq(10,200,20), name = "Citations")+
  ggthemes::theme_solarized_2()+
  theme(axis.title.x = element_blank())

```

\newpage

## Compare scholars

```{r, fig.cap="Authors and their cumulative citations"}
cs = scholar::compare_scholars(ids = tafiri$gs.id[-1])

cs %>% 
  ggplot(aes(x = year, y = total, color = name, shape = name))+
  geom_line() + 
  geom_point()+
  # facet_wrap(~name)+
  scale_x_continuous(breaks = seq(1990,2025,4))+
  geom_hline(yintercept = 50, linetype = 3, color = "red")+
  ggthemes::theme_solarized_2()+
  theme(axis.title.x = element_blank(), legend.position = c(.2,.8))+
  ggsci::scale_color_d3(name = "Author")+
  scale_shape(name = "Author")
  

```
\newpage
```{r, fig.cap="Cumulative number of citations by author"}

cs %>% 
  filter(name %in% c("Ismael A. Kimirei", "Mary Alphonce Kishe")) %>% 
  group_by(name) %>% 
  mutate(cumulative_cites = cumsum(cites)) %>% 
  ggplot(aes(x = year, y = cumulative_cites, color = name, shape = name))+
  geom_line() + 
  geom_point(size = 2)+
  # facet_wrap(~name, scales = "free_y")+
  scale_x_continuous(breaks = seq(2000,2025,4))+
  geom_hline(yintercept = 500, linetype = 3, color = "red")+
  ggthemes::theme_solarized_2()+
  theme(axis.title.x = element_blank(), legend.position = c(.2,.8))+
  ggsci::scale_color_d3(name = "Author")+
  scale_shape(name = "Author")
  
  
```

\newpage
## Impact factor

```{r}

if.kim = list()

for (i in 1:nrow(kim.pub)){

if.kim[[i]] = scholar::get_impactfactor(journals = kim.pub$journal[i])

}

if.kim %>% 
  bind_rows() %>% 
  drop_na() %>% 
  arrange(desc(ImpactFactor)) %>% 
  distinct(.keep_all = TRUE) %>% 
  kableExtra::kable(format = "latex", booktab = TRUE, caption = "Impact factor of journal 	IA Kimirei published") %>% 
  kableExtra::kable_styling(latex_options = "hold_position", font_size = 10)

```

\newpage

## Profile

```{r}
profile = scholar::get_profile(id = tafiri$gs.id[2])

as.data.frame(do.call(cbind, profile)) %>% 
  select(-c(i10_index,fields, id, affiliation))%>% 
  kableExtra::kable(format = "latex", booktab = TRUE, caption = "Google Scholar Profile of	IA Kimirei") %>% 
  kableExtra::kable_styling(latex_options = "hold_position", font_size = 10)

```

\newpage
## Co-authors

```{r, dev="pdf", fig.cap="The network coauthorship of Kimirei"}

ca = scholar::get_coauthors(id = tafiri$gs.id[2], n_coauthors = 10)

ca %>% 
  scholar::plot_coauthors(size_labels = 3)+
  ggthemes::theme_solarized_2()+
  theme()
```

\newpage

## h-index
The h-index is an author-level metric that measures both the productivity and citation impact of the publications, initially used for an individual scientist or scholar.

```{r, fig.cap="The h-index of authors at TAFIRI"}

h_index = list()

for (j in 2:nrow(tafiri)){

h_index[[j]] = scholar::predict_h_index(id = tafiri$gs.id[j]) %>% 
  mutate(name = tafiri$author[j])

}

h_index %>% 
  bind_rows() %>% 
  ggplot(aes(x = years_ahead, y = h_index, color = name))+
  geom_line()+
  geom_point()+
  scale_x_continuous(breaks = 0:10, labels = 2011:2021)+
  scale_y_continuous(name = "h-indes", breaks = scales::breaks_pretty(n = 8))+
  ggthemes::theme_solarized_2()+
  theme(axis.title.x = element_blank(), legend.position = c(.15,.72))+
  ggsci::scale_color_d3(name = "Author")+
  scale_shape(name = "Author")
  
```


```{r, eval=FALSE}

## get author id and plot the h-index

gsid = scholar::get_scholar_id(last_name = "Jackson", first_name = "Justo")

scholar::get_publications(id = gsid)

scholar::predict_h_index(id = gsid) %>% 
  ggplot(aes(x = years_ahead, y = h_index))+
  geom_line()+
  geom_point()+
  scale_x_continuous(breaks = 0:10, labels = 2011:2021)

```




